\documentclass{book}
\usepackage{hyperref}
\usepackage{unicode-math}
\setmathfont{texgyrepagella-math.otf}[math-style=TeX]
\usepackage{fontspec}
\setmainfont{TeX Gyre Pagella}
\usepackage{standalone}
\usepackage{biblatex}
\addbibresource{intro.bib}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{lemma}
\newtheorem*{example}{Example}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\title{Introduction to Commutative Algebra}
\author{M. F. ATIYAH \and I. G. MACDONALD}
\begin{document}
\frontmatter
\maketitle
\tableofcontents
\begin{refsection}
\chapter{Introduction}
Commutative algebra is essentially the study of commutative rings. Roughly
speaking, it has developed from two sources: (1) algebraic geometry and (2)
algebraic number theory. In (1) the prototype of the rings studied is the ring
$k[x_1, \cdots , x_n]$ of polynomials in several variables over a field $k$;
in (2) it is the
ring $\mathbf{Z}$ of rational integers. Of these two the algebro-geometric case is the more
far-reaching and, in its modern development by Grothendieck, it embraces much
of algebraic number theory. Commutative algebra is now one of the foundation
stones of this new algebraic geometry. It provides the complete local tools
for the subject in much the same way as differential analysis provides the tools
for differential geometry.

This book grew out of a course of lectures given to third year under-
graduates at Oxford University and it has the modest aim of providing a rapid
introduction to the subject. It is designed to be read by students who have had a
first elementary course in general algebra. On the other hand, it is not intended
as a substitute for the more voluminous tracts on commutative algebra such as
Zariski-Samuel \cite{zariski1960commutative} or Bourbaki \cite{bourbaki1961algebre}. We have concentrated on certain central
topics, and large areas, such as field theory, are not touched. In content we
cover rather more ground than Northcott \cite{northcott_1953} and our treatment is substantially
different in that, following the modern trend, we put more emphasis on modules
and localization.

The central notion in commutative algebra is that of a prime ideal. This
provides a common generalization of the primes of arithmetic and the points of
geometry. The geometric notion of concentrating attention ``near a point''
has as its algebraic analogue the important process of localizing a ring at a prime
ideal. It is not surprising, therefore, that results about localization can usefully
be thought of in geometric terms. This is done methodically in Grothendieck's
theory of schemes and, partly as an introduction to Grothendieck's work \cite{grothendieck1960elements},
and partly because of the geometric insight it provides, we have added schematic
versions of many results in the form of exercises and remarks.

The lecture-note origin of this book accounts for the rather terse style~ with
little general padding, and for the condensed account of many proofs. We have
resisted the temptation to expand it in the hope that the brevity of our presenta-
tion will make clearer the mathematical structure of what is by now an elegant
and attractive theory. Our philosophy has been to build up to the main theorems
in a succession of simple steps and to omit routine verifications.

Anyone writing now on commutative algebra faces a dilemma in connection
with homological algebra, which plays such an important part in modern
developments. A proper treatment of homological algebra is impossible within
the confines of a small book: on the other hand, it is hardly sensible to ignore it
completely. The compromise we have adopted is to use elementary homological
methods-exact sequences, diagrams, etc.-but to stop short of any results
requiring a deep study of homology. In this way we hope to prepare the ground
for a systematic course on homological algebra which the reader should undertake
if he wishes to pursue algebraic geometry in any depth.

We have provided a substantial number of exercises at the end of each
chapter. Some of them are easy and some of them are hard. Usually we have
provided hints, and sometimes complete solutions, to the hard ones. We are
indebted to Mr. R. Y. Sharp, who worked through them all and saved us from
error more than once.

We have made no attempt to describe the contributions of the many
mathematicians who have helped to develop the theory as expounded in this
book. We would, however, like to put on record our indebtedness to J.-P. Serre
and J. Tate from whom we learnt the subject, and whose influence was the
determining factor in our choice of material and mode of presentation.
\printbibliography[heading=subbibliography]
\end{refsection}
\chapter{Notation and Terminology}
Rings and modules are denoted by capital italic letters, elements of them by
small italic letters. A field is often denoted by $k$. Ideals are denoted by small
German characters. $\mathbf{Z, Q, R, C}$ denote respectively the ring of rational integers,
the field of rational numbers, the field of real numbers and the field of complex
numbers.

Mappings are consistently written on the \textit{left}, thus the image of an element $x$
under a mapping $f$ is written $f(x)$ and not $(x)f$. The composition of mappings
$f: X\to Y, g: Y\to Z$ is therefore $g\circ f$, not $f\circ g$.
A mapping $f: X\to Y$is \textit{injective} if $f(x_1) = f(x_2)$ implies $x_1 =
x_2$; surjective if $f(X) = Y$; bijective if both injective and surjective.

The end of a proof (or absence of proof) is marked thus \qedsymbol·
\newline

Inclusion of sets is denoted by the sign $\subseteq$. We reserve the sign
$\subset$ for strict inclusion. Thus $A\subset B$ means that $A$ is contained in $B$ and is not equal to $B$.
\mainmatter
\chapter{Rings and Ideals}
\chapter{Modules}
\chapter{Rings and Modules of Fractions}
\chapter{Primary Decomposition}
\input{4.tex}
\chapter{Integral Dependence and Valuations}
\chapter{Chain Conditions}
\chapter{Noetherian Rings}
\chapter{Artin Rings}
\chapter{Discrete Valuation Rings and Dedekind Domains}
\chapter{Completions}
\chapter{Dimension Theory}
\backmatter
\chapter{Index}
\end{document}
